Spectroscopic Characterization of New Er$^{3+}$ Host Crystals for Quantum Network Applications

### 2020-05-01 Draft.tex
Finish draft.

% Produce images?
\newtoggle{imgs}
% \toggletrue{imgs}
\togglefalse{imgs}

@@

\begin{titlepage}
  \singlespacing
  \begin{center}
    \vspace*{5mm}
    \Large{\textbf{Spectroscopic Characterization of New \erbium Host Crystals for Quantum Network Applications}}

@@

I've also had a number of wonderful non-research mentors over the years, all of whom have helped make me who I am. In particular, I want to thank Frau, Beuschlein, Mr. Davis, Mr. Hicks, Ruth Ochs, and especially my wonderful teachers Karen and Jo-Ann.

>>>>

% Produce images?
\newtoggle{imgs}
\toggletrue{imgs}
% \togglefalse{imgs}

@@

\begin{titlepage}
  \singlespacing
  \begin{center}
    \vspace*{5mm}
    \Large{\textbf{Spectroscopic Characterization of New \erbium Host Crystals for Quantum Networks}}

@@

I've also had a number of wonderful non-research mentors over the years, all of whom have helped make me who I am. In particular, I want to thank Frau, Beuschlein, Mr. Davis, Mr. Hicks, Mary Wraight, Ruth Ochs, and especially my wonderful clarinet teachers Karen and Jo-Ann.

Naturally, I have to thank everyone who played on the ECM recording of Steve Reich's Music for 18 Musicians, without whom I would have had to work to music with a melody, or, God forbid, words.

And my friends. My wonderful friends, who have supported me in so many ways over the years, and brought so much joy into my life, and inspired me at every turn to be a better version of myself. The old friends, Carl and Bernie, Lincoln, Paul, Corey, Erica, Rachel, Annie, Becca, Katie, Lizzy; and the new, Milena, Elliot, Sarah, Maria, Abigail, Audrey, Mal, Chris, Theodore, Jake, Shiye, and Ben. And, of course, everyone from Coffee Club, my family and my home on campus: Alex, Sara, Aemu, Ai Vy, Ali, Ava, BT, Bobo, Caitlin, Christine, Dylan, Ivan, Jack, Judy, Kat, Katherine, Linh, Lydia, Morgan, Philip, Sergio, Tessa, Alyssa, Maggie, Miranda, Ezra, Laura, Ishy, Emily, and Tai.

Finally, my family. My mom and dad, who have supported me unconditionally, and provided me with all the amazing opportunities that have led me to this point. Alison, who is as much a friend as an aunt. Max, whom I have employed as a research assistant on multiple occasions, and whose jazz chops I will never match but look forward to watching on the big stage. And to my grandparents, who have always believed I could do anything, and who will always make sure I never run out of cookies.
